---
title: "data605_hw10_wzhou"
author: "Wei Zhou"
date: "11/3/2019"
output: html_document
---


####Smith is in jail and has 1 dollar; he can get out on bail if he has 8 dollars. A guard agrees to make a series of bets with him. If Smith bets A dollars, he wins A dollars with probability .4 and loses A dollars with probability .6. Find the probability that he wins 8 dollars before losing all of his money if

####(a) he bets 1 dollar each time (timid strategy).

This is a gambler's ruin problem. 
Using the following equation: 
$$P=\frac{1-(\frac{q}{p})^i}{{1-(\frac{q}{p})^N}}$$

```{r}
q=0.6 
p=0.4 
N=8
i=1

P= (1-(q/p)^i)/(1-(q/p)^N)
P
```
Around 2.06% chance that he wins 8 dollars before losing all of his money if he bets 1 dollar each time.

####(b) he bets, each time, as much as possible but not more than necessary to bring his fortune up to 8 dollars (bold strategy).
Smith must win each time or lose everything upon the first lose. 
```{r}
P = 0.4^3
P
```
There is 6.4% chance that Smith will win 8 dollars before losing all of his money if using the bold strategy. 

####(c) Which strategy gives Smith the better chance of getting out of jail?
By comparing the probibilities of two strategies, it seems bold strategy has better chance to win 8 dollars before losing all of his money. 
