---
title: "Data605_hw15_WZHOU"
author: "Wei Zhou"
date: "12/8/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Problem 1

```{r}
x <- c(5.6, 6.3, 7, 7.7, 8.4)
y <- c(8.8, 12.4, 14.8, 18.2, 20.8)
r <- lm(y~x)
r
```

The regression model is $y = -14.8 + 4.257x$.


### Problem 2
Partial derivatives:

$f_x(x, y) = 24 - 6y^2$

$f_y(x, y) = -12xy - 24y^2$

$f_x$ and $f_y$ are never underfined. 

If $24-6y^2=0$, then $y^2 = 4$ and $y = \pm2$.

If $y=2$ and $-12xy - 24y^2=0$, then $-24x = 24\times 4$ and $x=-4$.

If $y=-2$ and $-12xy - 24y^2=0$, then $24x = 24\times 4$ and $x=4$.

Calculate $f(x, y)$.

$f(4,-2) = 24\times 4 - 6\times4\times (-2)^2 - 8 \times (-2)^3 = 64$

$f(-4,2) = 24\times (-4) - 6\times(-4)\times 2^2 - 8 \times 2^3 = -64$

**Two critical points**: $(4,-2,64)$ and $(-4, 2, -64)$.

Use Second Derivative test to determine if points are minimum, maximum or saddle. 

Second partial derivatives:

$f_{xx}=0$

$f_{yy}=-12x-48y$

$f_{xy}=-12y$

Then $D(x,y) = f_{xx} f_{yy}-f^2_{xy} = -(-12y)^2 = -144y^2$.

$D(x,y)<0$ for all $(x, y)$, so per Second Derivative Test, any critical point is a saddle point. 

### Problem 3

$$
\begin{split}
R(x,y) &= (81 - 21x + 17y)x + (40 + 11x - 23y)y \\
&= 81x-21x^2+17xy+40y+11xy-23y^2\\
&=81x+40y+28xy-21x^2-23y^2
\end{split}
$$

$R(2.3, 4.1)=81\times 2.3+40\times 4.1+28\times 2.3\times 4.1-21\times (2.3)^2-23\times (4.1)^2 = 116.62$

### Problem 4

Consider $x+y=96$, then $x=96-y$.

$$
\begin{split}
C(x,y) = C(96-y,y) &= \frac{1}{6} x^2 + \frac{1}{6} y^2 + 7x + 25y + 700 \\
&=\frac{1}{6} (96-y)^2 + \frac{1}{6} y^2 + 7\times (96-y) + 25y + 700 \\
&=\frac{1}{6}(y^2 - 192 y + 9216) + \frac{1}{6}y^2+672-7y+25y+700\\
&= \frac{1}{6}y^2 - 32y+1536+\frac{1}{6}y^2+18y+1372\\
&= \frac{1}{3}y^2 - 14y + 2908\\
&=C_1(y)
\end{split}
$$

$C_1'(y) = \frac{2}{3}y-14$

To find the minimal value consider $C_1'(y)=\frac{2}{3}y-14=0$, then $y=21$. Then $x=96-y=75$.

There should be 75 units produced in Los Angeles and 21 units produced in Denver.

### Problem 5

$$
\begin{split}
\int_2^4\int_2^4 (e^{8x+3y})\ dy\ dx &= \int_2^4 (\frac{1}{3}e^{8x+3y})|_2^4\ dx\\
&= \int_2^4 ((\frac{1}{3}e^{8x+12})-(\frac{1}{3}e^{8x+6}))\ dx\\
&= \int_2^4 \frac{1}{3}e^{8x+6}(e^6-1)\ dx\\
&=  \frac{1}{24}e^{8x+6}(e^6-1) |_2^4\\
&= \frac{1}{24}e^{32+6}(e^6-1)-\frac{1}{24}e^{16+6}(e^6-1)\\
&= \frac{1}{24}(e^6-1)(e^{38}-e^{22})\\
&= \frac{1}{24}(e^{44} - e^{38} - e^{28} + e^{22})
\end{split}
$$