---
title: "data605_hw9_WZHOU"
author: "Wei Zhou"
date: "10/27/2019"
output: html_document
---

##Page 363 Exercise 11

#####1. The price of one share of stock in the Pilsdorff Beer Company (see Exercise 8.2.12) is given by Yn on the n th day of the year. Finn observes that the differences Xn=Yn+1−Yn appear to be independent random variables with a common distribution having mean μ=0 and variance σ2=1/4. If Y1=100, estimate the probability that Y365 is

#####a. >=100 
This can be applied as a Gaussian random 
```{r}
mu = 0 
var = 1/4 
y = 365 
n = y-1 
sd = sqrt(var)

x = (100-100)/sqrt(n)

pnorm(x, mean = 0, sd = sd, lower.tail = FALSE)


```

#####b. >=110 
```{r}
x <- (110-100)/sqrt(n)
pnorm(x, mean = 0, sd = sd, lower.tail = FALSE)
```

#####c. >=120 
```{r}
x <- (120-100)/sqrt(n)
pnorm(x, mean = 0, sd = sd, lower.tail = FALSE)
```

#####Question 2 
 

For binomial distribution, $P(X=k) = {n \choose k} p^k q^{n-k}$, where $q=1-p$.

The moment generating function is $M_X(t)=(q+pe^t)^n$.

First moment: $M'_X(t) = n(q+pe^t)^{n-1}pe^t$.
The expected value is the first moment evaluated at $t=0$:
$$
\begin{split}
E(X)=M'_X(0) &= n(q+pe^0)^{n-1}pe^0\\
&= n(q+p)^{n-1}p\\
&= np(1-p+p)^{n-1}\\
&= np1^{n-1}\\
&=np
\end{split}
$$
Second moment:  $M''_X(t) = n(n-1)(q+pe^t)^{n-2}p^2 e^{2t}+n(q+pe^t)^{n-1}pe^t$.
Evaluate the second moment at $t=0$:
$$
\begin{split}
E(X^2)=M''_X(0) &= n(n-1)(q+pe^0)^{n-2}p^2 e^0+n(q+pe^0)^{n-1}pe^0\\
&= n(n-1)(1-p+p)^{n-2}p^2+n(1-p+p)^{n-1}p\\
&= n(n-1)p^2+np
\end{split}
$$
Variance: $V(X)=E(X^2)-E(X)^2$:
$$
\begin{split}
V(X) &= n(n-1)p^2+np-n^2p^2 \\
&= np((n-1)p+1-np) \\
&= np(np-p+1-np) \\
&= np(1-p) \\
&= npq
\end{split}
$$
Then we got: $E(X)=np$ and $V(X)=npq$.

Reference:  http://math.arizona.edu/~tgk/464_10/chap4_9_29.pdf.


##### Problem 3 Calculate the expected value and variance of the exponential distribution using the moment generating function.


For exponential distribution, $f(x)=\lambda e^{-\lambda x}$.
The moment generating function is $M_X(t)=\frac{\lambda}{\lambda-t}, t<\lambda$.
Using WolframAlpha, we get $M'_X(t) = \frac{\lambda}{(\lambda-t)^2}$ and $M''_X(t) = \frac{2\lambda}{(\lambda-t)^3}$.
Expected value:
$$
\begin{split}
E(X)=M'_X(0) &= \frac{\lambda}{(\lambda-0)^2} \\
&= \frac{\lambda}{\lambda^2}\\
&= \frac{1}{\lambda}
\end{split}
$$
Variance:
$$
\begin{split}
V(X) = E(X^2)-E(X)^2 &= M''_X(0)-M'_X(0)^2 \\
&=\frac{2\lambda}{(\lambda-0)^3} - \frac{1}{\lambda^2}\\
&=\frac{2\lambda}{\lambda^3} - \frac{1}{\lambda^2}\\
&=\frac{2}{\lambda^2} - \frac{1}{\lambda^2}\\
&=\frac{1}{\lambda^2}
\end{split}
$$
