---
title: "data605_hw5_WZHOU"
author: "Wei Zhou"
date: "9/22/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Choose independently two numbers B and C at random from the interval [0, 1] with
uniform density. Prove that B and C are proper probability distributions.
Note that the point (B,C) is then chosen at random in the unit square.

Create random variables B, C for 1000000 times
```{r}
n = 1000000
B = runif(n,0,1)
C = runif(n,0,1)

```


Prove B and C are proper probability distributions: 

```{r}
hist(B, probability = TRUE)
hist(C, probability = TRUE)
```


Find the probability that

### (a) B + C < 1/2.
```{r}
sum_BC=B+C
P = sum(sum_BC<0.5) / 1000000
```
The probability that the sum of B and C falls below 12 is about `r P`.

```{r}
hist(sum_BC,probability = TRUE)
```

### (b) B×C < 1/2
```{r}
prod_bc = B*C
P = sum(prod_bc<0.5) / 1000000
```
The probability that the production of B and C falls below 12 is about `r P`.

```{r}
hist(prod_bc,probability = TRUE)
```


### (c) |B−C|<1/2
```{r}
abs_b_c = abs(B-C)
P = sum(abs_b_c<0.5) / 1000000
```
The probability is about `r P`.

```{r}
hist(abs_b_c,probability = TRUE)
```


### (d) max{B,C}<1/2
```{r}
BC_df=as.data.frame(cbind(B,C))
BC_df = transform(BC_df, max = pmin(B,C))
P=sum(BC_df$max<0.5)/1000000
      
```
The probability is about `r P`.
```{r}
hist(BC_df$max)
```

