---
title: "data606_hw2_WZhou"
author: "Wei Zhou"
date: "9/15/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#### What is the rank of matrix A ? 
```{r}
A = matrix(c(1,-1,0,5,2,0,1,4,3,1,-2,-2,4,3,1,-3),4,4)
A
```

```{r}
qr(A)$rank
```
Since each row is linear independent from other rows, the rank of the matrix is 4. 

#### Given an mxn matrix where m > n, what can be the maximum rank? The mini- mum rank, assuming that the matrix is non-zero?
The maximum rank can be equal or less than n, the minimum rank of non-zero matrix is 1. 


#### What is the rank of matrix B?
```{r}
B = matrix(c(1, 3, 2, 2, 6, 4, 1, 3, 2),3,3)
B
qr(B)$rank
```
```{r}
2* B[1,] == B[3,]
3* B[1,] == B[2,]
```
Since each row is not linearly independent with other rows, the rank of B is 1. 

####Compute the eigenvalues and eigenvectors of the matrix A. You’ll need to show your work. You’ll need to write out the characteristic polynomial and show your solution.

$$\mathbf{A} = \left[\begin{array}
{rrr}
1 & 2 & 3 \\
0 & 4 & 5 \\
0 & 0 & 6
\end{array}\right]
$$

$$
\lambda E-A= 
 \left[\begin{array}
{rrr}
\lambda - 1 & -2 & -3 \\
0 & \lambda -4 & -5 \\
0 & 0 & \lambda -6
\end{array}\right] \\
det(\lambda E-A) = (\lambda -1 )(\lambda - 4)(\lambda -6 ) = 0 \\
\lambda^{3}-11\lambda^{2}+34\lambda - 24 = 0 \\
Eigenvalue: \lambda_1 = 6 , \lambda_2 = 4, \lambda_3 = 1 \\
$$
Now we need to use the eigenvalue to calculate the eigenvectors: 

$$
(\lambda_1 I-A)h_1 = 0 \\
 \left[\begin{array}
{rrr}
5 & -2 & -3 \\
0 & 2 & -5 \\
0 & 0 & 0
\end{array}\right]h_1 =
\left[\begin{array}
{rrr}
0 \\
0  \\
0\end{array}\right] \\
h_1 = \left[\begin{array}
{rrr}
1.6 \\
2.5 \\
1\end{array}\right] \\ 
$$
$$
(\lambda_2 I-A)h_2 = 0 \\
 \left[\begin{array}
{rrr}
3 & -2 & -3 \\
0 & 0 & -5 \\
0 & 0 & -2
\end{array}\right]h_2 =
\left[\begin{array}
{rrr}
0 \\
0  \\
0\end{array}\right] \\
h_2 = \left[\begin{array}
{rrr}
1 \\
1.5 \\
0 \end{array}\right] \\
$$

$$
(\lambda_3 I-A)h_3 = 0 \\
 \left[\begin{array}
{rrr}
1 & -2 & -3 \\
0 & -3 & -5 \\
0 & 0 & -5
\end{array}\right]h_2 =
\left[\begin{array}
{rrr}
0 \\
0  \\
0\end{array}\right] \\
h_3 = \left[\begin{array}
{rrr}
1 \\
0 \\
0 \end{array}\right] \\ 
$$
