---
title: "Data605_HW7_WZHOU"
author: "Wei Zhou"
date: "10/13/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##HW #7 - Distribution & Densities,Expected Value & Variance

####1.Let X1,X2,…Xn be n mutually independent random variables, each of which is uniformly distributed on the integers from 1 to k. Let Y denote the minimum of the Xis. Find the distribution of Y.

Answer:

Y = Minimum(Xis)

Since each random variable Xi has k possibilities, the total possible number of assignment of the whole number collection is `k^n` 

Let's analyze the situation when `Y=1`. To get the number of possibilties that `Y=1`, we can exclude the number of possibilities that `Xi!=1` out of `k^n`. 

Thus, the number of possibilities is `k^n - (k-1)^n`.  
`P(Y=1) =  (k^n - (k-1)^n) / k^n`

Similarly, when Y=2, we need to exclude the number of possibilities that `Xi=2` and `Xi<=1` from `k^n`. 

`P(Y=2) =[ k^n - (k-2)^2 - [(k^n - (k-1)^n)] ]/ k^n`

`       = ((k-1)^n - (k-2)^n)/k^n`

When Y = a, then `P(Y=a) = ((k-a+1)^n - (k-a)^n) / k^n`



####2. Your organization owns a copier (future lawyers, etc.) or MRI (future doctors). This machine has a manufacturer’s expected lifetime of 10 years. This means that we expect one failure every ten years. (Include the probability statements and R Code for each part.).

a. What is the probability that the machine will fai after 8 years?. Provide also the
expected value and standard deviation. Model as a geometric. (Hint: the probability is
equivalent to not failing during the first 8 years..)

```{r}
library('stats')
pfail = 1/10 
psucc = 1-pfail 
n = 8 

result = 1- pgeom(n-1,pfail)
```
The probability that the machine will fai after 8 years is `r result`

```{r}
expect_value = 1/pfail
```

Expected Value: `E(X) =` `r expect_value`

```{r}
sd = sqrt(psucc/pfail^2)
```
Standard deviation is `r sd`


b. What is the probability that the machine will fail after 8 years?. Provide also the
expected value and standard deviation. Model as an exponential. 

```{r}
n= 8
lambda = 1/10 

p_expo = pexp(n,lambda,lower.tail=FALSE)

```
The probability that the machine will fail after 8 years is `r p_expo`


```{r}
expect_value = 1/lambda 
```
Expect vaue is `r expect_value`

```{r}
sd = sqrt(1/lambda^2)
```
Standard Deviation is `r sd`

c. What is the probability that the machine will fail after 8 years?. Provide also the
expected value and standard deviation. Model as a binomial. (Hint: 0 success in 8
years)

```{r}
b= 8 
p = 1/10 
q = 1- p 
k = 0

p_binomial = dbinom(k,n,p)
```

The probability that the machine will fail after 8 years is `r p_binomial`

```{r}
expect_value = n*p 
```
Expected value is `r expect_value`

```{r}
sd = sqrt(n*p*q)
```
Standard deviation is `r sd`


d. What is the probability that the machine will fail after 8 years?. Provide also the
expected value and standard deviation. Model as a Poisson


```{r}
lambda <- 8/10
k <- 0

p_poison= ppois(0,lambda = .8 )

```
The probability that the machine will fail after 8 years is `r p_poison`

```{r}
expect_value = 8/10 
```
Expected value is `r expect_value`

```{r}
sd = sqrt(expect_value)
```
Standard deviation is `r sd`




