---
title: "data605_hw4_WZHOU"
author: "Wei Zhou"
date: "9/22/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Problem Set 1
```{r}
A <- matrix(c(1,2,3,-1,0,4), nrow = 2, ncol = 3, byrow = TRUE)
A

```
```{r}
A_t = t(A)
A_t
```

Computing X and Y
```{r}
X = A%*%A_t
Y = A_t%*%A
X
Y
```

Now we get the Eigenvalues and Eigenvectors of X 
```{r}
X_eigen = eigen(X)
X_eigen
X_eigenvalue = X_eigen$values
X_eigevector = X_eigen$vectors
```

```{r}
Y_eigen = eigen(Y)
Y_eigen
Y_eigenvalue = Y_eigen$values
Y_eigevector = Y_eigen$vectors
```

Using SVD function to calculate the left singular values of A
```{r}
A_left_svd = svd(A, nu = 2, nv = 0)
A_left_svd$u
```

By comparing the result, we found the column 1 differs by a negative, otherwise the same. 
```{r}
A_left_svd$u
X_eigevector
```

Using SVD function to calculate the right singular values of A
```{r}
A_right_svd = svd(A, nu = 0, nv = 3)
A_right_svd$v
```

By comparing the result, we found the column 1,3  differs by a negative, otherwise the same. This also means that the singular value vectors form an orthonormal set like the eigenvectors.
```{r}
A_right_svd$v
Y_eigevector
```

As for eigenvalues, you will find the values are the same. 
```{r}
(A_right_svd$d)^2
(A_left_svd$d)^2
X_eigenvalue
Y_eigenvalue
```


### Problem Set 2
```{r}

inverse_matrix <- function(A){
  #Create identiy matrix with rows and columns equal to A
  C <- diag(1,nrow(A),ncol(A))
   for (i in 1:nrow(A)) { 
        for (j in 1:ncol(A)){ 
          #Calucate the value for each element 
          Pij <- A[-i,-j]
          C[i,j] <- ((-1)^(i+j))*det(Pij)
        }
   }
  #Use the transpose of the created matrix C and the determinant of the input matrix A to get the inverse
  return(t(C)/det(A))
}

```

Sample
```{r}
A <- matrix(sample(0:9, 25,  replace = TRUE), nrow=5, ncol=5)
inverse_matrix(A)
```


