---
title: "weizhou_hw2"
author: "Wei Zhou"
date: "9/6/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Question Set 1
####1.1
Show that AT A # AAT in general. (Proof and demonstration.)

Proof: 
Assum A is a 3\*2 matrix, then AT is 2\*3 matrix. 

A \* AT should be a 3\*3 matrix, whereas AT\*A is a 2\*2 matrix

Thus, A \* AT not equal to AT\*A in general

Demonstration
```{r}
a = matrix(c(1, 4, 7, 2, 5, 8, 3), nrow=3, ncol=2)
a
t(a)
a%*%t(a)
t(a)%*%a
```

####1.2 
For a special type of square matrix A, we get AT A = AAT Under what conditionscould this be true?

When a matrix is Symmetric matrix or antisymmetric matrix or orthogonal matrix, AT \* A = A \* AT 



## Problem Set 2 


```{r}
sfunc <- function (n, i, x) {
  s <- diag (n)
  s [i, i] <- x
  return (s)
}

tfunc <- function (n, i, j, x) {
  t <- diag (n)
  t [i, j] <- x
  return (t)    
}

gaussMatrixForward <- function (a, verbose = TRUE) {
  n <- nrow (a)
    for (i in 1 : n) {
        a <- sfunc (n, i, 1 / a[i, i]) %*% a
        if (i == n) {
            break ()
        }
        for (j in (i + 1) : n) {
            a <- tfunc (n, j, i, - a[j, i]) %*% a
        }
    }
    return (a)
}

LU_decomp <- function (a) {
  n <- nrow (a)
    g <- gaussMatrixForward (cbind (a, diag (n)))
  h <- gaussMatrixForward (cbind (g[, n + 1 : n], diag (n)))
  return (list (L = h[, n + 1 : n], U = g [, 1 : n]))
}
```

```{r}
set.seed (12345)
print (a <- matrix (sample (16), 4, 4))
print (lu <- LU_decomp (a))
```


```{r}
library(matrixcalc)
A <- matrix( c ( 1, 2, 2, 1 ), nrow=2, byrow=TRUE)
luA <- lu.decomposition( A )
luA
```